Tree-structured neural networks revisited

### 2016-03-08 writing/hard_stack_paper/paper.tex
Paper updates.
Added citation.

\item Speed issues
\begin{itemize}
\item Efficient batched computation is a crucial enabling technology in allowing NNs to be used on large datasets. Since NNs require large datasets to be able to model complex problems like language understanding, this is crucial in NLP.
\item Tree structured neural networks can't be batched. As the schematic in Figure~\ref{fig:batching:bad} indicates, different sentences are assigned different trees, and there is no straightforward way of aligning these trees to synchronize computation in the conventional style of implementation.
\item Our proposed model builds on ideas from transition-based parsing to build a model which implements the same computations as a tree-structured model, but which can be efficiently batched. See Figure~\ref{fig:batching:good}.

@@

There has been a fairly long history of work on building neural-network based parsers that use the core operations and data structures from transition-based parsing \cite{henderson2004discriminative,emami2005neural,titov2010latent,buys2generative,chen2014,dyer-EtAl:2015:ACL-IJCNLP}. In addition, there has been recent work \cite{zhang2016top,dyer2016rnn} proposing models designed primarily for generative language modeling tasks that use these structures as well. To our knowledge, our model is the first to use these structures for the purpose of sentence interpretation, rather than parsing or generation.

>>>>

\item Speed issues
\begin{itemize}
\item Efficient batched computation is a crucial enabling technology in allowing NNs to be used on large datasets. Since NNs require large datasets to be able to model complex problems like language understanding, this is crucial in NLP.
\item Tree structured neural networks can't be batched. As the schematic in Figure~\ref{fig:batching:bad} indicates, different sentences are assigned different trees, and there is no straightforward way of aligning these trees to synchronize computation in the conventional style of implementation.
\item Our proposed model builds on ideas from transition-based parsing to build a model which implements the same computations as a tree-structured model, but which can be efficiently batched.

@@

There has been a fairly long history of work on building neural-network based parsers that use the core operations and data structures from transition-based parsing \cite{henderson2004discriminative,emami2005neural,titov2010latent,buys2generative,chen2014,dyer-EtAl:2015:ACL-IJCNLP,kiperwasser2016easy}. In addition, there has been recent work \cite{zhang2016top,dyer2016rnn} proposing models designed primarily for generative language modeling tasks that use these structures as well. To our knowledge, our model is the first to use these structures for the purpose of sentence interpretation, rather than parsing or generation.
